quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Application figure title

```{r}
#| fig-cap: ""
#| label: fig-limb-mse
#| out-width: 100%

>>>>

```{r}
#| fig-cap: "Assessing which of the 6 NLDR layouts on the limb3k data  (shown in @fig-nldrlayouts) is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f)."
#| label: fig-limb-mse
#| out-width: 100%

### 2025-05-12 paper-quollr.tex
Application figure title

\begin{figure}
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/fig-limb-mse-1} \end{figure}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/fig-limb-mse-1} \caption{Assessing which of the 6 NLDR layouts on the limb3k data  (shown in @fig-nldrlayouts) is the better representation using RMSE for varying binwidth ($a_1$). Colour  used for the lines and points in the left plot and in the scatterplots represents NLDR layout (a-f).}\label{fig:fig-limb-mse}
\end{figure}
